---
title: "Conf_on_MB"
output: html_document
---
#Fig 3. D & H. At the file "Conf_MFMB.Rmd", there are codes for visualization and statistics on the regression results. The regression analysis was done with Matlab codes, written by "Rani Moran", in the "Matlab-codes/Conf_MFMB_regression.m".

We compared the influence on confidence on MB behavior in the next trial in three drug conditions, the analysis was done in Rani Moran's code at Matlab, in the below i just show the plots and statistical tests.
```{r setup, include=FALSE}
source("libs/Librarries.R") 
source("libs/plot/compare_mbmf_reg_plot.R")
source("libs/plot/mytheme.R")# just for better visualization of plots

```


```{r}
#_pro , _dop , and _plac refer to the drug conditions
confmb_pro = readMat("data/Data_in_matlab/tot_confMB_pro.mat")  # fixed+random, 30 subs
confmb_plac = readMat("data/Data_in_matlab/tot_confMB_plac.mat")
confmb_dop = readMat("data/Data_in_matlab/tot_confMB_dop.mat")
confmbpro = confmb_pro$tot.effects.with.intercept
confmbplac = confmb_plac$tot.effects.with.intercept
confmbdop = confmb_dop$tot.effects.with.intercept
confmbdrugs = list(confmbpro,confmbplac,confmbdop)
```

#Section 2.2.2
```{r}
### Comparing Betas, influence of regressors, between drug conditions
coef=4
nsub=30
subs = c(1:30)
tot_2opt = c(confmbdrugs[[1]][coef,subs],confmbdrugs[[2]][coef,subs],confmbdrugs[[3]][coef,subs])
drugname = c(rep("pro", nsub), rep("plac", nsub), rep("dop", nsub))
meta = data.frame(tot_2opt,drugname = as.factor(drugname) , subs= as.factor(subs))#
# Repeated measure anova
res = aov(tot_2opt~drugname+ Error(subs/drugname) , data = meta)
summary(res)


# the lmer orders the conditions from A-Z, and take the first one as the control condition, it is teh reason that i added A,B,C before our drug names
drugname = c(rep("Bpro", nsub), rep("Aplac", nsub), rep("Cdop", nsub))
meta = data.frame(tot_2opt,drugname = as.factor(drugname), subs = as.factor(subs))
# lmer
res = lmer(tot_2opt ~ drugname+ (1|subs) , data = meta)
summary(res)

# Posthoc tests
# between pro and plac
wilcox.test(confmbdrugs[[1]][coef,subs],confmbdrugs[[2]][coef,subs] )
# between dop and plac
wilcox.test(confmbdrugs[[3]][coef,subs],confmbdrugs[[2]][coef,subs] )
# between pro and dop
wilcox.test(confmbdrugs[[1]][coef,subs],confmbdrugs[[3]][coef,subs] )
```
 
# Fig. 3H
```{r}
coef=4
effectmf= data.frame(confmbdrugs[[1]][coef,],confmbdrugs[[2]][coef,],confmbdrugs[[3]][coef,])
p1 = compare_mbmf_reg_plot(effectmf)
p1
```


# Interaction of confidence and MF, Figure 3D

```{r}
confmf_pro = readMat("data/Data_in_matlab/tot_confMF_pro.mat")  # fixed+random, 30 subs
confmf_dop = readMat("data/Data_in_matlab/tot_confMF_dop.mat")
confmf_plac = readMat("data/Data_in_matlab/tot_confMF_plac.mat")
confmfpro = confmf_pro$tot.effects.with.intercept
confmfdop = confmf_dop$tot.effects.with.intercept
confmfplac = confmf_plac$tot.effects.with.intercept
confmfdrugs = list(confmfpro, confmfplac, confmfdop)
```

#Section 2.2.2
```{r}
### Comparing Betas, influence of regressors, between drug conditions
coef=4
#25,26,28
nsub=30
subs = c(1:30)
tot_2opt = c(confmfdrugs[[1]][coef,subs],confmfdrugs[[2]][coef,subs],confmfdrugs[[3]][coef,subs])
drugname = c(rep("pro", nsub), rep("plac", nsub), rep("dop", nsub))
meta = data.frame(tot_2opt,drugname = as.factor(drugname), subs = as.factor(subs) )
res = aov(tot_2opt~drugname +Error(subs/drugname) , data = meta)
summary(res)

# the lmer orders the conditions from A-Z, and take the first one as the control condition, it is teh reason that i added A,B,C before our drug names
drugname = c(rep("Bpro", nsub), rep("Aplac", nsub), rep("Cdop", nsub))
meta = data.frame(tot_2opt,drugname = as.factor(drugname), subs = as.factor(subs))
# lmer
res = lmer(tot_2opt ~ drugname+ (1|subs) , data = meta)
summary(res)

# between pro and plac
wilcox.test(confmfdrugs[[1]][coef,subs],confmfdrugs[[2]][coef,subs] )
# between dop and plac
wilcox.test(confmfdrugs[[3]][coef,subs],confmfdrugs[[2]][coef,subs] )
# between pro and dop
wilcox.test(confmfdrugs[[1]][coef,subs],confmfdrugs[[3]][coef,subs] )

```

# Fig. 3D
```{r}
coef=4
effectmf= data.frame(confmfdrugs[[1]][coef,],confmfdrugs[[2]][coef,],confmfdrugs[[3]][coef,])
p1 = compare_mbmf_reg_plot(effectmf)
p1
```

