---
title: "Hmeta_drugs"
output: html_document
date: "2023-02-09"
---
#Fig 2. A & B & C. At the file "Hmeta_drugs.Rmd". These codes call the functions from "HMeta/R"
```{r}
source("libs/Librarries.R") 
source("HMeta/R/trials2counts.R")
source("HMeta/R/fit_metad_groupcorr.R")
source("libs/plot/compare_mbmf_reg_plot.R")
source("libs/plot/mytheme.R")# just for better visualization of plots

```


#The data from perceptual task was read and fitted according to Hmeta package from Fleming,S.
```{r}
ndrug = 3
nt_bl =25
nsub = 30
nblk = 8
nRatings = 6
nrat= 2*6 # we have 2 response for choice
drug = readRDS("data/drug.rds") # order of drug days for each subject
adressdrug = "data/complete/" # data from perceptual tasks
completesubs = c(102:112, 114:117, 119:133) 

nrg_s1 = list()
nrg_s2 = list()
for (dru in 1:ndrug){
  ns1=matrix(0,nrow =nrat,ncol = nsub )
  ns2=matrix(0,nrow =nrat,ncol = nsub )
  for(sub in 1:nsub){
    subid = completesubs[sub]
    drugpos = drug[sub,dru]
    data = readMat(paste0(adressdrug,subid,"/","perceptData",subid,"-",drugpos,".mat"))
    response = c()
    rating = c()
    stimID = c()
    for (blk in 1:nblk){
      adress_subj = data$DATA[,,blk]$results[,,1]
      response = c(response, adress_subj$response)
      rating = c(rating, adress_subj$responseConf)
      rating[rating==0]= mean(rating[rating!=0]) # putting the average confidence for trials that there was no response.
      rating  = floor((rating-50)*((nRatings-1)/50) + 1)
      stimID_subj = rep(0,nt_bl)
      stimID_subj[adress_subj$correct==1]= adress_subj$response[adress_subj$correct==1]
      wrongres = adress_subj$response[adress_subj$correct==0]
      stimID_subj[adress_subj$correct==0]= (wrongres%%2)+1
      stimID = c(stimID,stimID_subj)

    } #blk
    response = response-1
    stimID  =  stimID -1
    a = trials2counts(stimID, response, rating,nRatings, padAmount = 0,padCells=0) # preparing the vectors including frequency of each rate for each response.
    nRp_S1 <- a[[1]]
    nRp_S2 <- a[[2]]
    ns1[,sub]= nRp_S1
    ns2[,sub]= nRp_S2
    
  } #sub
 
  nrg_s1[[dru]]= ns1
  nrg_s2[[dru]]= ns2
  
} #dru

nR_S1 = nrg_s1
nR_S2 = nrg_s2
output <- fit_metad_groupcorr(nR_S1 = nR_S1, nR_S2 = nR_S2) # Fitting to Hmeta, for all three groups considering to correlation between three groups

```

#The code to check HDI and Rhat (not a main result in the draft)
# Reported at section 4.3, Data Analysis (Rhat)
```{r}
output = readRDS("data/hmeta_depndent_3group.rds")

# Rhat 
Value <- gelman.diag(output, confidence = 0.95)
Rhat <- data.frame(conv = Value$psrf)


```

#plot the group posterior distributions for comparison, Figure 2B
```{r}
###plot M.Ratio for all three groups
output = readRDS("data/hmeta_depndent_3group.rds")
mcmcsample <- ggs(output)
mu1 = exp(mcmcsample$value[which(mcmcsample$Parameter=="mu_logMratio[1]")])
mu2 = exp(mcmcsample$value[which(mcmcsample$Parameter=="mu_logMratio[2]")])
mu3 = exp(mcmcsample$value[which(mcmcsample$Parameter=="mu_logMratio[3]")])

# Reported at section 2.1; 80% for pro, 60% for dop (L-DOPA)
length(which(mu1-mu3<0))/length(mu1-mu3)
length(which(mu2-mu3>0))/length(mu2-mu3)

randcoef = c(mu1,mu3,mu2)
nsam = length(mu1)
drugname = c(rep("Prop",nsam),rep("Plac",nsam),rep("Dop",nsam))
df = data.frame(randcoef ,drugname)
df$drugname = factor(df$drugname,levels = c("Prop","Plac","Dop"))

p =ggplot(df,aes(x = randcoef , fill  = drugname))+
  geom_density(alpha = 0.5)+scale_fill_manual(values=c("#F8766D", "#00BFC4","#619CFF"))+xlab("Meta-cognitive ability")+ylab("Density")+
    labs(title = "")+ xlim(c(0,2))+
    theme_bw( ) + mytheme
p
```


#To see the number of samples that are higher in one group relative to another one (not an critical code)
# Sectionn 2.1 of the paper
```{r}
### increase by Dopamine and decrease by Prop subject by subject.
output = readRDS("data/hmeta_depndent_3group.rds")
mcmcsample <- ggs(output)
nsub=30
ndrag = 2
nmethod = 2
ratio_dif_indiv = array(0, c(nsub,ndrag,nmethod)) #prop and Dop minus Place
for (sub in 1:nsub){
    mu1 = mcmcsample$value[which(mcmcsample$Parameter==paste0("Mratio[",sub,",1]"))]
    mu2 = mcmcsample$value[which(mcmcsample$Parameter==paste0("Mratio[",sub,",2]"))]
    mu3 = mcmcsample$value[which(mcmcsample$Parameter==paste0("Mratio[",sub,",3]"))]
    
    
    ratio_dif_indiv[sub,1,1] = length(which(mu1-mu3<0))/length(mu1-mu3)
    ratio_dif_indiv[sub,2,1] = length(which(mu2-mu3>0))/length(mu2-mu3)
    ratio_dif_indiv[sub,1,2] = mean(mu1-mu3)
    ratio_dif_indiv[sub,2,2] = mean(mu2-mu3)
}


length(which(mu1-mu3<0))/length(mu1-mu3)
length(which(mu2-mu3>0))/length(mu2-mu3)

```


#plot that compares Hmeta across different groups for each subject, Figure 2C
```{r}
#_pro , _dop , and _plac refer to the drug conditions
### increase vy Dopamine and decrease by Prop subject by subject.
output = readRDS("data/hmeta_depndent_3group.rds")
mcmcsample <- ggs(output)
nsub=30
ndrug = 3
meta_indiv = array(0, c(nsub,ndrug)) #prop and Dop minus Place
for (sub in 1:nsub){
    meta_indiv[sub,1] = mean(mcmcsample$value[which(mcmcsample$Parameter==paste0("Mratio[",sub,",1]"))]) #pro
    meta_indiv[sub,2] = mean(mcmcsample$value[which(mcmcsample$Parameter==paste0("Mratio[",sub,",2]"))]) #dop
    meta_indiv[sub,3] = mean(mcmcsample$value[which(mcmcsample$Parameter==paste0("Mratio[",sub,",3]"))]) #plac
    
}

p=compare_mbmf_reg_plot(cbind( meta_indiv[,1],meta_indiv[,3],meta_indiv[,2]))
p
```

#Test to show infleunce of drug conditions on individual estimations of Hmeta
# Section 2.1
```{r}
### Comparing the individual posteriors from Hmeta, between drug conditions
nsub = 30
subs = c(1:nsub)
tot_2opt = c(meta_indiv[,1],meta_indiv[,3] ,meta_indiv[,2])
drugname = c(rep("pro", nsub), rep("plac", nsub), rep("dop", nsub))
meta = data.frame(tot_2opt,drugname = as.factor(drugname), subs = as.factor(subs))
# Repeated measure anova
res = aov(tot_2opt~drugname+ Error(subs/drugname) , data = meta) 
summary(res)

# the lmer orders the conditions from A-Z, and take the first one as the control condition, it is teh reason that i added A,B,C before our drug names
drugname = c(rep("Bpro", nsub), rep("Aplac", nsub), rep("Cdop", nsub))
meta = data.frame(tot_2opt,drugname = as.factor(drugname), subs = as.factor(subs))
# lmer
res = lmer(tot_2opt ~ drugname+ (1|subs) , data = meta)
summary(res)

# between pro and plac
wilcox.test(meta_indiv[,1],meta_indiv[,3] )
# between dop and plac
wilcox.test(meta_indiv[,2],meta_indiv[,3] )
# between pro and dop
wilcox.test(meta_indiv[,1],meta_indiv[,2] )

```


#compare performance under drugs, Fig 2A
```{r}
ndrug = 3
nt_bl =25
nsub = 30
nblk = 8
perf = matrix(0, nrow = ndrug, ncol=nsub) # two is for storring mean and se
rt = matrix(0, nrow = ndrug, ncol=nsub) # two is for storring mean and se
conf = matrix(0, nrow = ndrug, ncol=nsub) # two is for storring mean and se
drug = readRDS("data/drug.rds")
adressdrug = "data/complete/"
completesubs = c(102:112, 114:117, 119:133)  # 4 last added

for (dru in 1:ndrug){
  for(sub in 1:nsub){
    subid = completesubs[sub]
    drugpos = drug[sub,dru]
    data = readMat(paste0(adressdrug,subid,"/","perceptData",subid,"-",drugpos,".mat"))
    perfsub = c()
    rtsub = c()
    confsub = c()
    for (blk in 1:nblk){
      adress_subj = data$DATA[,,blk]$results[,,1]
      perfsub = c(perfsub, adress_subj$correct)
      rtsub = c(rtsub, adress_subj$rt)
      confsub = c(confsub, adress_subj$responseConf)
      
    } #blk
    perf[dru,sub] = mean(perfsub)
    rt[dru,sub] = mean(rtsub)
    conf[dru,sub] = mean(confsub)
  } #sub
} #dru

effectmb= data.frame(perf[1,],perf[3,],perf[2,])
p2 = compare_mbmf_reg_plot(effectmb)
p2
```

# Section 2.1
```{r}
#Compare performance in Perceptual task across drug conditions
  allcoef = c(perf[1,],perf[3,],perf[2,])#confcor_med
  drugname = c(rep("pro",nsub),rep("plac",nsub),rep("dop",nsub))
  subs = rep(c(1:nsub), 3)
  meta = data.frame(allcoef,drugname = as.factor(drugname), subs= as.factor(subs))
  resaov = aov(allcoef~drugname+Error(subs/drugname) , data = meta)
  summary(resaov)
  
  # the lmer orders the conditions from A-Z, and take the first one as the control condition, it is teh reason that i added A,B,C before our drug names
drugname = c(rep("pro", nsub), rep("plac", nsub), rep("dop", nsub))
meta = data.frame(allcoef ,drugname = as.factor(drugname), subs = as.factor(subs))
# lmer
res = lmer(allcoef ~ drugname+ (1|subs) , data = meta)
summary(res)
  
```

# Section 2.1
```{r}
#Compare confidence in Perceptual task across drug conditions
  allcoef = c(conf[1,],conf[3,],conf[2,])#confcor_med
  drugname = c(rep("pro",nsub),rep("plac",nsub),rep("dop",nsub))
  subs = rep(c(1:nsub), 3)
  meta = data.frame(allcoef,drugname = as.factor(drugname), subs= as.factor(subs))
  resaov = aov(allcoef~drugname+Error(subs/drugname) , data = meta)
  summary(resaov)
  
  # the lmer orders the conditions from A-Z, and take the first one as the control condition, it is teh reason that i added A,B,C before our drug names
drugname = c(rep("Bpro", nsub), rep("Aplac", nsub), rep("Cdop", nsub))
meta = data.frame(allcoef ,drugname = as.factor(drugname), subs = as.factor(subs))
# lmer
res = lmer(allcoef ~ drugname+ (1|subs) , data = meta)
summary(res)

```

