---
title: "MB/MF_contribution, drug conditions"
output: html_document
---
#Fig 3. A & F & C & G. At the file "MBMF_contribution.Rmd", there are codes for visualization and statistics on the regression results. The regression analysis was done with Matlab codes, written by "Rani Moran", in the "Matlab-codes/MBMF_contributions_regression.m".

```{r setup, include=FALSE}
source("libs/Librarries.R") 
source("libs/plot/compare_mbmf_reg_plot.R")
```

```{r}
#_pro , _dop , and _plac refer to the drug conditions
# four rows are related to intercept and MB, prob and their interaction
promf = readMat("data/Data_in_matlab/tot_MFprop_30.mat")
placmf = readMat("data/Data_in_matlab/tot_MFplac_30.mat")
dopmf = readMat("data/Data_in_matlab/tot_MFdop_30.mat")
promb = readMat("data/Data_in_matlab/tot_regparam_pro.mat")
placmb = readMat("data/Data_in_matlab/tot_regparam_plac.mat")
dopmb = readMat("data/Data_in_matlab/tot_regparam_dop.mat")
promf = promf$tot.effects.with.intercept
placmf = placmf$tot.effects.with.intercept
dopmf = dopmf$tot.effects.with.intercept
promb = promb$tot.effects.with.intercept
placmb = placmb$tot.effects.with.intercept
dopmb = dopmb$tot.effects.with.intercept 
```

#MB contribution in Placebo condition, Figure 3F
```{r}
placmb_fix = readMat("data/Data_in_matlab/coef_mbreg_plac.mat")
placsemb = readMat("data/Data_in_matlab/se_mbreg_plac.mat")
means = c(placmb_fix$coeff.MB[1,1],placmb_fix$coeff.MB[2,1],placmb_fix$coeff.MB[3,1])
se = c(placsemb$coeff.MB.SE[1,1],placsemb$coeff.MB.SE[2,1],placsemb$coeff.MB.SE[3,1])


dt = data.frame(ind = c(1:3), index = as.numeric(means), ss = as.numeric(se))
                                              
   p= ggplot(dt,aes(x = ind, y = index)) +
    scale_y_continuous(breaks = c(-0.5,0,0.5,1),limits = c(-0.5,2.1))+
    geom_errorbar(aes(ymin = index-ss, ymax = index+ss), width =.0000001) +
    geom_point()+
    scale_x_continuous(breaks = 1:3,labels = c("Rew","Prob","Int"),limits = c(0.8,3.2))+
    xlab("")+ylab("beta")+
    theme_bw(base_size = 20) + 
    theme(
    axis.title.y = element_text(hjust = 0.5),
          axis.line = element_line(colour = "black"),
          panel.border = element_blank(),
          panel.grid = element_blank(),
          panel.background = element_blank(),
          legend.background=element_blank()
          )
   p
```



# Distribution plots to compare MB and MF contributions, Figures 3 C & G
```{r}
effectmf= data.frame(promf[2,],placmf[2,],dopmf[2,])
p1 = compare_mbmf_reg_plot(effectmf)
p1

effectmb= data.frame(promb[2,],placmb[2,],dopmb[2,])
p2 = compare_mbmf_reg_plot(effectmb)
p2
```

# Section 2.2.1 , MF
```{r}
### Comparing Betas, influence of regressors, between drug conditions
coef=2
nsub=30
subs = c(1:nsub)
tot_2opt = c(promf[coef,subs],placmf[coef,subs], dopmf[coef,subs])
drugname = c(rep("pro", nsub), rep("plac", nsub), rep("dop", nsub))
meta = data.frame(tot_2opt,drugname = as.factor(drugname), subs = as.factor(subs) )
res= aov(tot_2opt ~ drugname + Error(subs/drugname) , data = meta) 
summary(res)

# the lmer orders the conditions from A-Z, and take the first one as the control condition, it is teh reason that i added A,B,C before our drug names
drugname = c(rep("Bpro", nsub), rep("Aplac", nsub), rep("Cdop", nsub))
meta = data.frame(tot_2opt,drugname = as.factor(drugname), subs = as.factor(subs))
# lmer
res = lmer(tot_2opt ~ drugname+ (1|subs) , data = meta)
summary(res)

```

# Section 2.2.1, MB
```{r}
### Comparing Betas, influence of regressors, between drug conditions
coef=2
nsub=30
subs = c(1:nsub)
tot_2opt = c(promb[coef,subs],placmb[coef,subs], dopmb[coef,subs])
drugname = c(rep("pro", nsub), rep("plac", nsub), rep("dop", nsub))
meta = data.frame(tot_2opt,drugname = as.factor(drugname), subs = as.factor(subs) )
res= aov(tot_2opt~drugname+ Error(subs/drugname) , data = meta) 
summary(res)

# the lmer orders the conditions from A-Z, and take the first one as the control condition, it is teh reason that i added A,B,C before our drug names
drugname = c(rep("Bpro", nsub), rep("Aplac", nsub), rep("Cdop", nsub))
meta = data.frame(tot_2opt,drugname = as.factor(drugname), subs = as.factor(subs))
# lmer
res = lmer(tot_2opt ~ drugname+ (1|subs) , data = meta)
summary(res)

# between pro and plac
wilcox.test(promb[coef,subs],placmb[coef,subs])
# between dop and plac
wilcox.test(dopmb[coef,subs],placmb[coef,subs])
# between pro and dop
wilcox.test(promb[coef,subs],dopmb[coef,subs])
```
